

# references {#ref}



Below is a Div containing three child Divs side by side. The Div
in the middle is empty, just to add more space between the left
and right Divs.

:::: {style="display: flex;"}

::: {.col data-latex="{0.45\textwidth}"}

```{r, c1, echo=FALSE, out.width="100%"}
par(mar = c(4, 4, .2, .1))
plot(cars, pch = 19)
```

Yet she does have a kind of respect for the creatures. “Their behavior clearly works; there are a lot of harvester ant colonies out there, more every year,” she observes. “I deeply admire their harvester-ant-ness, the richness of their responses to a world so alien to me.”

:::

::: {.col data-latex="{0.05\textwidth}"}
\ 
<!-- an empty Div (with a white space), serving as
a column separator -->
:::

::: {.col data-latex="{0.45\textwidth}"}


Yet she does have a kind of respect for the creatures. “Their behavior clearly works; there are a lot of harvester ant colonies out there, more every year,” she observes. “I deeply admire their harvester-ant-ness, the richness of their responses to a world so alien to me.”


```{r, c3, echo=FALSE, out.width="100%"}
par(mar = c(4, 4, .2, .1))
plot(cars, pch = 19)
```

:::
::::


---
# random YAML comment
---


```{r bibDatabase, include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

